Current and future constraints on primordial magnetic fields

### 2016-10-21 pmf.tex
a

>>>>

Finally, we consider if searches for PMFs introduce new requirements on the knowledge to which the instrumental beam or overall calibration of the experiments must be known. 
We parametrize the beam uncertainty as a fractional uncertainty on the FWHM of the Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
We find negligible ($<$\,1\%) shifts in the forecasted uncertainty for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
The PMF constraints are insensitive to beam and calibration uncertainty.
